\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-02-07 article.tex
Added graphs for all techniques, minor refactoring

  It has, however, recently been observed that a bias towards the right leg
  exist. The study by Gibbs\cite{rlb} show that there is a total of 152 kicks
  in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
  kicks are with the left leg. This means that 56\% of the kicks are with the
  right leg, and 44\% with the left leg.

  The work by Gibbs focused on kicks in all patterns, whereas this article
  examines patterns Chon-Ji to Juche. Looking at kicks in said patterns using
  Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
  the right leg, and 30 kicks are with the left leg. Roughly 58\% of the kicks
  are with the right leg, and about 42\% with the left. Thus, the right leg
  bias still holds.

@@

  Our findings show that of 519 techniques, 256 (49\%) are with the left arm
  and 263 (51\%) with the right arm (Table \ref{tab:table1}). Looking at the
  total amount of techniques, only 7 techniques (about 1\%) separates an even
  distribution to both sides.

@@

      Blocks    & 148   & 133 \\
      Punches   &  60   &  71 \\
      Strikes   &  34   &  38 \\
      Thrusts   &  14   &  21 \\
    \hline

      \textbf{Total}   & \textbf{256}   & \textbf{263} \\
      \hline
    \end{tabular}
    \caption{Number of techniques per arm by category.}
    \label{tab:table1}
  \end{table}

@@

  In terms of category distribution, there are more blocks with the left side
  than there are with the right side. A side effect is that there are more
  attacks with the right side, than with the left side (Table
  \ref{tab:table2}).

@@

      Blocks    &  57.81\%    &  50.57\% \\
      Punches   &  23.44\%    &  27.00\% \\
      Strikes   &  13.28\%    &  14.45\% \\
      Thrusts   &   5.47\%    &   7.98\% \\
    \hline
    \end{tabular}
    \caption{Percent distribution of techniques per arm by category.}
    \label{tab:table2}
  \end{table}

>>>>

  It has, however, recently been observed that a bias towards the right leg
  exist. The study by Gibbs\cite{rlb} show that there is a total of 152 kicks
  in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
  kicks are with the left leg. This means that 56 \% of the kicks are with the
  right leg, and 44 \% with the left leg.

  The work by Gibbs focused on kicks in all patterns, whereas this article
  examines patterns Chon-Ji to Juche. Looking at kicks in said patterns using
  Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
  the right leg, and 30 kicks are with the left leg. Roughly 58 \% of the
  kicks are with the right leg, and about 42 \% with the left. Thus, the right
  leg bias still holds.

@@

  Our findings show that of 519 techniques, 256 (49 \%) are with the left arm
  and 263 (51 \%) with the right arm (Table \ref{tab:table1}). Looking at the
  total amount of techniques, only 7 techniques (about 1 \%) separates an even
  distribution to both sides.

@@

      Blocks    & 148   & 133 \\
      Punches   &  60   &  71 \\
      Strikes   &  34   &  38 \\
      Thrusts   &  14   &  21 \\

      \hline
      \textbf{Total}   & \textbf{256}   & \textbf{263} \\
      \hline

    \end{tabular}
    \caption{Number of techniques per arm by category.}
    \label{tab:table1}
  \end{table}

@@

  In terms of category distribution, there are more blocks with the left side
  than there are with the right side. There are, therefore, more attacks with
  the right side, than with the left side (Table \ref{tab:table2}, Figure
  \ref{fig:techniques_all}).

@@

      Blocks    &  57.81 \%    &  50.57 \% \\
      Punches   &  23.44 \%    &  27.00 \% \\
      Strikes   &  13.28 \%    &  14.45 \% \\
      Thrusts   &   5.47 \%    &   7.98 \% \\

      \hline
      \textbf{Total}   & \textbf{100 \%}   & \textbf{100 \%} \\
      \hline

    \end{tabular}
    \caption{Percent distribution of techniques per arm by category.}
    \label{tab:table2}
  \end{table}

  % Distribution of techniques by category
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/techniques_all}
    \caption{Distribution of techniques by category.}
    \label{fig:techniques_all}
  \end{figure}

\clearpage
